IRS-Aided SWIPT:\\Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model

### 2021-08-12 assets/waveform_wpt_multisine.tex
:bento: Update assets

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,3.198in)},
scale only axis,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
ymax=1,
ytick={0, 1},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.5,1.03)}, anchor=south, legend columns=2, legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
1	0.000179640013528533\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{IRS: {\boldmath${s}$}$_{\mathrm{P}}$}

@@

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,2.513in)},
scale only axis,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
ymax=1,
ytick={0, 1},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	3.79500700797208e-06\\
2	4.08912055500049e-06\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.49290916575988e-05\\
2	1.5984007495811e-05\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,1.828in)},
scale only axis,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ymax=1,
ytick={0, 1},
ylabel style={font=\color{white!15!black}},
ylabel={Waveform amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	1.7047574186968e-05\\
2	5.43653691324513e-05\\
3	5.45654270177953e-05\\
4	0.643758338055473\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.36848368645437e-05\\
2	2.47445070835246e-05\\
3	2.69448998495505e-05\\
4	0.887691893042722\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,1.143in)},
scale only axis,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
ymax=4.47213595499958,
ytick={0, 2, 4},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.0867788582585271\\
2	0.354584687432597\\
3	0.978311956865194\\
4	1.00526014633142\\
5	1.77421254564815\\
6	1.81146146011329\\
7	2.39316922290828\\
8	2.39637542235877\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.0902176300392888\\
2	0.346545381997116\\
3	0.920392715728033\\
4	1.00603974348273\\
5	1.68636658487784\\
6	1.88211529376329\\
7	2.36040788303805\\
8	2.46040714408403\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,0.458in)},
scale only axis,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
ymax=4.47213595499958,
ytick={0, 2, 4},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.0464370103565898\\
2	0.0888998754115983\\
3	0.182477468723257\\
4	0.351067698858224\\
5	0.586511157963407\\
6	0.614337078252067\\
7	0.810319773242887\\
8	0.860994249853337\\
9	1.10132170987082\\
10	1.14707079761106\\
11	1.39883656543765\\
12	1.41535986846215\\
13	1.61724209266044\\
14	1.62252465458191\\
15	1.72749872908311\\
16	1.73005229015507\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.0510852453116461\\
2	0.0931309188028207\\
3	0.185327611314329\\
4	0.340208570070271\\
5	0.54797982875002\\
6	0.640935330786823\\
7	0.791412536150533\\
8	0.84579943866006\\
9	1.06112099796475\\
10	1.16793555562456\\
11	1.33939925851288\\
12	1.47707717171709\\
13	1.57685904146789\\
14	1.6756197826186\\
15	1.71965928671636\\
16	1.75172173644803\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%

>>>>

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,3.198in)},
scale only axis,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
ymax=1,
ytick={0, 1},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.5,1.03)}, anchor=south, legend columns=2, legend cell align=left, align=left, draw=white!15!black},
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
1	0.000179640013528533\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{IRS: {\boldmath${s}$}$_{\mathrm{P}}$}

@@

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,2.513in)},
scale only axis,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
ymax=1,
ytick={0, 1},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	3.79500700797208e-06\\
2	4.08912055500049e-06\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.49290916575988e-05\\
2	1.5984007495811e-05\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,1.828in)},
scale only axis,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ymax=1,
ytick={0, 1},
ylabel style={font=\color{white!15!black}},
ylabel={Waveform amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	1.7047574186968e-05\\
2	5.43653691324513e-05\\
3	5.45654270177953e-05\\
4	0.643758338055473\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.36848368645437e-05\\
2	2.47445070835246e-05\\
3	2.69448998495505e-05\\
4	0.887691893042722\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,1.143in)},
scale only axis,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
ymax=4.47213595499958,
ytick={0, 2, 4},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.0867788582585271\\
2	0.354584687432597\\
3	0.978311956865194\\
4	1.00526014633142\\
5	1.77421254564815\\
6	1.81146146011329\\
7	2.39316922290828\\
8	2.39637542235877\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.0902176300392888\\
2	0.346545381997116\\
3	0.920392715728033\\
4	1.00603974348273\\
5	1.68636658487784\\
6	1.88211529376329\\
7	2.36040788303805\\
8	2.46040714408403\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,0.458in)},
scale only axis,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
ymax=4.47213595499958,
ytick={0, 2, 4},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.0464370103565898\\
2	0.0888998754115983\\
3	0.182477468723257\\
4	0.351067698858224\\
5	0.586511157963407\\
6	0.614337078252067\\
7	0.810319773242887\\
8	0.860994249853337\\
9	1.10132170987082\\
10	1.14707079761106\\
11	1.39883656543765\\
12	1.41535986846215\\
13	1.61724209266044\\
14	1.62252465458191\\
15	1.72749872908311\\
16	1.73005229015507\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.0510852453116461\\
2	0.0931309188028207\\
3	0.185327611314329\\
4	0.340208570070271\\
5	0.54797982875002\\
6	0.640935330786823\\
7	0.791412536150533\\
8	0.84579943866006\\
9	1.06112099796475\\
10	1.16793555562456\\
11	1.33939925851288\\
12	1.47707717171709\\
13	1.57685904146789\\
14	1.6756197826186\\
15	1.71965928671636\\
16	1.75172173644803\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%
